---
title: "xrayr: dynamic and static xray quantification"
author: "Brian B. Avants, Elliott Greenblatt, et. al."
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteIndexEntry{xrayr for DCR}
    \usepackage[utf8]{inputenc}
---

Focus on chest radiography.

```{r global options, include=FALSE}
library( knitr )
knitr::opts_chunk$set(collapse = T, comment = "#>")

```{r libs}
library( xrayr )
library( magrittr )
library( ANTsRCore )
library( ANTsR )
```

# Utilities

## Motion correction

Motion correction.

```{r mot}
temp1 = resampleImage( ri(1), 4 )
temp2 = resampleImage( ri(2), 4 )
tarspace = makeImage( c( dim( temp1 ), 2 ) )
pdcr = mergeListToNDImage( tarspace, list( temp1, temp2 ) )
reg = timeSeriesMotionCorrect( temp1, pdcr )
```


## Segmentation

JLF

```{r jlf}
```

## Denoising



# Applications

## Super resolution

Motion correction.

```{r sr}
sup = timeSeriesSuperResolution( temp1, reg, method = 'average' )
```



## Functional studies

decomposition

```{r perf}
```



## References

Tanaka etc
