---
title: "xrayr: dynamic and static xray quantification"
author: "Brian B. Avants, Elliott Greenblatt, et. al."
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteIndexEntry{xrayr for DCR}
    \usepackage[utf8]{inputenc}
---

Focus on chest radiography.

```{r global options, include=FALSE}
library( knitr )
knitr::opts_chunk$set(collapse = T, comment = "#>")

```{r libs}
library( xrayr )
library( magrittr )
library( ANTsRCore )
library( ANTsR )
```

# Utilities

## Motion correction

Motion correction.

```{r mot}
temp1 = resampleImage( ri(1), 4 )
temp2 = resampleImage( ri(2), 4 )
tarspace = makeImage( c( dim( temp1 ), 2 ) )
pdcr = mergeListToNDImage( tarspace, list( temp1, temp2 ) )
reg = timeSeriesMotionCorrect( temp1, pdcr )
```


## Segmentation

JLF

```{r jlf}
```

## Denoising



# Applications

## Super resolution

Real data.

### PROCEDURE OUTLINE
1.  downsample-upsample to create simulated data
2.  motion correct
3.  avg/sharpen to get super-res estimate
  
procedure would differ slightly in a pure testing context
ie it would be iterated until convergence
but ultimately should probably be replaced with convnets


```{r sr,eval=FALSE}
################
library( ANTsR )
library( xrayr )
baseDir = "/mnt/c/Users/bavants/projects/kmXrayPilotData/superRes/lowres/"
id = "0070"
fns = Sys.glob( paste0( baseDir, "*", id, "*mhd" ) )
img = antsImageRead( fns[1] )
limg = splitNDImageToList( img )
mimgLow = list()
ww = c( 5, 1:4,6:8) # arbitrarily chosen
limg = limg[ ww[ -1 ] ] # some stuff nearby
for ( k in 1:length( limg ) ) {
  # downsample by factor of X for training data
  X = 2.7
  hiSpc = antsGetSpacing( limg[[ k ]])
  loSpc = hiSpc * X
  moLo = resampleImage( limg[[ k ]], loSpc, useVoxels = F )
  mimgLow[[ k ]] = moLo
  }

# map time series
reg = timeSeriesMotionCorrect( tar, mimgLow )

ct = 1
wts = seq( from=-2, to=2, by=0.1 )
errs = rep( NA, length( wts )) 
for ( wt in wts ) {
  sup = timeSeriesSuperResolution( tar, reg, 'sharpen', param1 = wt )
  print( paste( wt,   MSE( tar, sup ) ) )
  errs[ ct ] = MSE( tar, sup )
  ct = ct + 1
  }
plot( wts, errs )

```



## Functional studies

decomposition

```{r perf}
```



## References

Tanaka etc
